Effects of Trauma Life Support Training Programs on Patient Outcomes: A Pilot Cluster Randomised Trial

### 2024-10-09 pilot-publication/manuscript.Rmd
Compile revised manuscript

---
## compile with:
## Rscript -e "rmarkdown::render('manuscript.Rmd', output_format = 'all')"
title: "Effects of Trauma Life Support Training Programs on Patient Outcomes: A Pilot Cluster Randomised Trial"
author: Trauma life support training Effectiveness Research Network (TERN) collaborators
bibliography: bibliography.bib
csl: nature.csl
output:
    bookdown::pdf_document2:
      toc: false
      number_sections: false
    md_document: default
    bookdown::word_document2:
      toc: false
      number_sections: false
      reference_docx: "reference.docx"
---

>>>>

---
## compile with:
## Rscript -e "rmarkdown::render('manuscript.Rmd', output_format = 'all')"
title: "Effects of Trauma Life Support Training Programs on Patient Outcomes: A Pilot Cluster Randomised Trial"
author: Trauma life support training Effectiveness Research Network (TERN) collaborators
bibliography: bibliography.bib
csl: nature.csl
output:
    md_document: default
    bookdown::word_document2:
      toc: false
      number_sections: false
      reference_docx: "reference.docx"
#    bookdown::pdf_document2:
#      toc:false
#      number_sections:false
---
